Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
clean up

# Display three-way interaction terms
threeway_rows <- grep("ever_lapse.*:dr_severity.*:any_treatment", 
                      pooled_results$Term, value = FALSE)

if (length(threeway_rows) > 0) {
  threeway_results <- pooled_results[threeway_rows, c("Term", "Estimate", "SE", "P_Value", "OR")]
  threeway_results$P_Value <- format.pval(threeway_results$P_Value, digits = 4, eps = 0.0001)

  kable(threeway_results,
        caption = "Three-Way Interaction Terms (Pooled Across Imputations)",
        row.names = FALSE,
        digits = 4)
}
```

@@

## Predicted Probabilities Table

```{r predicted-probs}
# Simplified approach - just show probabilities from first imputation
# (In a full analysis, would pool across all imputations)

message("\nCalculating predicted probabilities...")

# Use first imputation for demonstration
emm_probs <- emmeans(models[[1]], 
                     ~ ever_lapse_binary | dr_severity * any_treatment,
                     type = "response",
                     weights = "proportional")

# Convert to data frame
prob_df <- as.data.frame(emm_probs)

# Check what columns we actually have
if (n_imputations > 0) {
  message("Available columns in prob_df: ", paste(names(prob_df), collapse = ", "))
}

# Create simple probability table - find the right column names
prob_col_candidates <- c("prob", "response", "emmean", "estimate", "predicted", "fitted")
prob_col_name <- NULL
for (candidate in prob_col_candidates) {
  if (candidate %in% names(prob_df)) {
    prob_col_name <- candidate
    break
  }
}

# If we still don't have it, try grep
if (is.null(prob_col_name)) {
  prob_col_idx <- grep("prob|response|emmean|estimate", names(prob_df), ignore.case = TRUE)[1]
  if (!is.na(prob_col_idx)) {
    prob_col_name <- names(prob_df)[prob_col_idx]
  }
}

# Check what factor columns we have
factor_cols <- c("dr_severity", "any_treatment", "ever_lapse_binary")
available_factor_cols <- factor_cols[factor_cols %in% names(prob_df)]

if (!is.null(prob_col_name) && length(available_factor_cols) >= 3) {
  prob_table <- prob_df |>
    mutate(
      Probability = round(.data[[prob_col_name]], 3)
    ) |>
    dplyr::select(all_of(available_factor_cols), Probability)

  # Try to pivot if we have the lapse column
  if ("ever_lapse_binary" %in% names(prob_table)) {
    prob_table <- prob_table |>
      pivot_wider(names_from = ever_lapse_binary, values_from = Probability)
  }
} else {
  # Create empty table if we can't process
  prob_table <- data.frame(
    Message = "Could not create probability table - missing required columns"
  )
  message("Warning: Missing columns for probability table. Available columns: ", 
          paste(names(prob_df), collapse = ", "))
}

kable(prob_table,
      caption = "Predicted Probability of Vision Impairment by Subgroup",
      row.names = FALSE)
```

>>>>

# Three-way interaction terms are included in the model
# but not displayed individually as they are not meaningful on their own
# See subgroup effects and marginal effects sections for interpretation
```

@@
